Manuscript

### 2024-05-30 Manuscript.qmd
added author info
Cleaned Data for dtw

---
title: "Manuscript"
format: html
output:
  units: cm
---

@@

# Files

MgCa <- read_csv(here("data","MgCa.csv")) %>% 
  arrange(sampleID)
D18O <- read_csv(here("data","d18O.csv")) %>% 
    arrange(sampleID)

# Check overlaps
# Find common sample IDs
intersect(MgCa$sampleID, D18O$sampleID)

# Find sample IDs only in MgCa
setdiff(MgCa$sampleID, D18O$sampleID)

# Find sample IDs only in D18O
setdiff(D18O$sampleID, MgCa$sampleID)

@@

>>>>

---
title: "Manuscript"
format: html
author: Niklas Hausmann
output:
  units: cm
---

@@

# Files  
read_csv(D18O,here("data","D18O.csv"))
read_csv(MgCa,here("data","MgCa.csv"))

# Check overlaps
# Find common sample IDs
intersect(MgCa$sampleID, NMgCa$sampleID)

# Find sample IDs only in MgCa
setdiff(MgCa$sampleID, NMgCa$sampleID)

# Find sample IDs only in D18O
setdiff(NMgCa$sampleID, MgCa$sampleID)

@@

```{r}
#| label: DTW Analysis

Samples <- unique(MgCa$sampleID)

# Initialize an empty list to store the results of shell_dtw for each sample
dtw_results <- list()

Corr_data <- tibble()

sample <- Samples[6]

# for (sample in Samples) {
  temp_D18O <- D18O %>% 
    filter(sampleID == sample) %>% 
    select(d18O) %>% 
    rename(d18o = d18O) %>% 
    mutate(sample_seq = row_number())

  temp_MgCa <- MgCa %>% 
    filter(sampleID == sample) %>% 
    filter(!(sampleID=="ND-1016-4"&dist<0.3)) %>% 
    select(mg_ca) %>% 
    mutate(sample_seq = row_number())

  # Apply shell_dtw to the temp dataframes and store the result in the list
  dtw_results[[sample]] <- shell_dtw_data(temp_D18O, temp_MgCa)

   # Add the sampleID column to temp_data
  temp_data <- dtw_results[[sample]]$data %>% 
    mutate(sampleID = sample)

  # Append temp_data to Corr_data
  Corr_data <- bind_rows(Corr_data, temp_data)
# }

```{r}
#| label: DTW Results 
#| fig-cap: 
#| fig-height:
#| fig-width:

P_all <- Corr_data %>% 
  pivot_wider(values_from = "value",names_from = "proxy") %>% 
  ggplot()+
  aes(d18o,mg_ca,col=sampleID)+
  geom_point(show.legend = FALSE)+
  labs(x=expression("‰ δ" ^ "18" * "O [VPDB]"),y="Mg/Ca intensity ratio")+
  stat_smooth(aes(fill = sampleID,col=sampleID), method = "lm", formula = y~x,show.legend = FALSE) +
  # stat_regline_equation(label.x = 2, #label.y = 32
  #   aes(label =  paste(after_stat(eq.label), after_stat(adj.rr.label), sep = "~~~~")),
  #   formula = y~x
  # ) +
  scale_colour_manual(values = c("#007f7f", "#d73027", "#ffc100", "black", "#1f78b4", "#33a02c", "#ff7f00", "#6a3d9a", "#e74c3c", "#2ecc71", "#f39c12")) +
scale_fill_manual(values = c("#007f7f", "#d73027", "#ffc100", "black", "#1f78b4", "#33a02c", "#ff7f00", "#6a3d9a", "#e74c3c", "#2ecc71", "#f39c12"))
# Expanded colour palette with 6 additional colours
# Updated colour palette with 4 new replacements for the last colours
# Refined colour palette with 3 additional colours
# c("#007f7f", "#d73027", "#ffc100", "black", "#1a9850", "#542788", "#3288bd", "#99d8c9")

P_individual <- P_all+
  facet_wrap(~sampleID,ncol=2)+#ylim(0.15,NA)+
  ggpubr::stat_regline_equation(label.x = 1.5, label.y = 0.25,
    aes(label =  paste(after_stat(eq.label), after_stat(adj.rr.label), sep = "~~~~")),show.legend = FALSE,
    formula = y~x
  )

P_all/P_individual+plot_layout(heights = c(0.5,0.5))
